\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{geometry}

% Settings
\geometry{margin=1in}
\AtBeginEnvironment{adjustwidth}{\partopsep0pt} % remove space before adjustwidth environment
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0.15cm} % set column separation
\pagenumbering{gobble} % no page numbering

\begin{document}

\begin{center}
  {\LARGE \textbf{Charles Alders}} \\
  Santa Cruz, CA 95062 \\
  \href{mailto:charliealders26@gmail.com}{charliealders26@gmail.com} \\
  \href{https://github.com/char26}{GitHub}
\end{center}

\vspace{0.5cm}

\begin{flushleft}
  CS\&E graduate student at UC Santa Cruz. Self-motivated learner and Software Engineer. Experience in distributed database systems, development operations, RESTful API development, and software/database testing. Passionate about all things data and technology.
\end{flushleft}

\section*{Skills}
Python, JavaScript/TypeScript, Java, Kotlin, C++, Apache Cassandra, CQL/SQL, AWS, Google Cloud, bash/zsh, Linux (Debian/NixOS), Git/GitHub, Docker, Flask, Graph Databases, Jenkins

\section*{Education}
\begin{flushleft}
  \textbf{M.S. Computer Science \& Engineering} \hfill Sep 2024 - Dec 2025 (Expected) \\
  University of California, Santa Cruz - Santa Cruz, CA
\end{flushleft}

\begin{flushleft}
  \textbf{B.S. Business Administration: Project Management} \hfill Aug 2018 - Dec 2022 \\
  Regis University - Denver, CO
\end{flushleft}
\section*{Experience}

\begin{flushleft}
  \textbf{SDE Intern} \hfill Jun 2025 - Present \\
  Amazon - Bellevue, WA \\
  AWS Keyspaces - Data Storage, Access, and Management Team
\end{flushleft}

\begin{flushleft}
  \textbf{Teaching Assistant} \hfill Jan 2025 - Jun 2025 \\
  University of California, Santa Cruz - Santa Cruz, CA \\
  CSE123B - Engineering Design Project II - Spring 2025
  \begin{itemize}
    \item Assisted five groups of 4-6 students with cloud infrastructure and web application setup for two-quarter-long prototype IoT devices.
  \end{itemize}
  CSE111 - Advanced Programming (C++) - Winter 2025
  \begin{itemize}
    \item Guided 50+ undergraduate students through a quarter-long C++ group project.
    \item Performed code reviews with groups of 4-6 students, giving feedback on code quality.
  \end{itemize}
\end{flushleft}

\begin{flushleft}
  \textbf{Software Engineer Intern} \hfill Jan 2025 - May 2025 \\
  Archon.gg - Remote (Contract)
  \begin{itemize}
    \item Significantly improved accuracy of LLM-powered code generator for warcraftlogs.com by taking trainingcode example count from 5 to 50+.
  \end{itemize}
\end{flushleft}

\begin{flushleft}
  \textbf{Software Engineer} \hfill Apr 2023 - Jan 2025 \\
  X5E, Inc. - Remote (Contract)
  \begin{itemize}
    \item Primarily focused on the development of open source distributed DBMS based on Conflict-Free Replicated Data Types, with TypeScript and Python implementations.
    \item Implemented additional data stores, data structures, integration tests, unit tests, and database performance tests in both Python and TypeScript.
    \item Oversaw all development operations by utilizing GitHub actions, Docker, and Jenkins to automate builds and tests across multiple operating systems and architectures.
    \item Automated package publishing and documentation generation utilizing language specific tools (e.g., readthedocs).
    \item Created and optimized algorithms for data retrieval, creation, and synchronization.
  \end{itemize}
\end{flushleft}
\end{document}
